### 2022-11-02 doc/manuscript/translocation.qmd
Small edits to manuscript

We used exome capture methods to compare genomes of frogs in populations with different histories of Bd exposure, in an effort to putative genes under selection that are linked to reduced frog susceptibility to Bd-caused lethal and sub-lethal effects. Specifically, we compared genomes of frogs that have never experienced a Bd-caused epizootic ("Bd-naive") versus populations that experienced a Bd epizootic during the past several decades and have since recovered to varying degrees ("recovering). These populations persist in an enzootic state, characterized by high Bd prevalence and Bd infection intensities (load) in adults that are well below the level expected to cause frog mortality. Bd-exposure histories of these populations are based on a decade or more of data from VES and Bd surveillance using skin swabbing.

@@

Translocations of *R. sierrae* were conducted in Yosemite National Park (California, USA) as part of an effort to reestablish populations of this endangered species. We identified donor populations from which adult frogs could be collected using several years of visual encounter surveys (VES) and skin swab collections (Knapp et al. 2016). Results indicated that these populations contained several hundred *R. sierrae* adults and hundreds or thousands of tadpoles, and had recovered from previous Bd-caused declines. Bd prevalence donor populations is high and Bd infection intensity (load) is below the level at which frog mortality is predicted (calculate mean prevalence and load). Recipient sites to which frogs were translocated were chosen based on previous *R. sierrae* presence (determined from VES and/or museum records) or characteristics that suggested high quality habitat for this species (Knapp 2005).

@@

In this model we ignore density-dependent recruitment because we were interested in the growth of the population from an initial reintroduction and whether this growth was sufficient to prevent extinction over 50 years following the introduction. We also did not directly consider the dynamics of Bd in this model. We made this decision because i) all translocated populations are infected with Bd at high prevalence ii) host density does not seem to play a significant role in multi-year Bd infection dynamics in this system. Thus, ignoring Bd infection dynamics and instead assuming all host vital rates are in the presence of high Bd prevalence significantly simplifies the model without much loss of realism.

>>>>

We used exome capture methods to compare genomes of frogs in populations with different histories of Bd exposure, in an effort to identify putative genes under selection that are linked to reduced frog susceptibility to Bd-caused lethal and sub-lethal effects. Specifically, we compared genomes of frogs that have never experienced a Bd-caused epizootic ("Bd-naive") versus populations that experienced a Bd epizootic during the past several decades and have since recovered to varying degrees ("recovering). These populations persist in an enzootic state, characterized by high Bd prevalence and Bd infection intensities (load) in adults that are well below the level expected to cause frog mortality. Bd-exposure histories of these populations are based on a decade or more of data from VES and Bd surveillance using skin swabbing.

@@

Translocations of *R. sierrae* were conducted in Yosemite National Park (California, USA) as part of an effort to reestablish populations of this endangered species. We identified donor populations from which adult frogs could be collected using several years of visual encounter surveys (VES) and skin swab collections (Knapp et al. 2016). Results indicated that these populations contained several hundred *R. sierrae* adults and hundreds or thousands of tadpoles, and had recovered from previous Bd-caused declines. Bd prevalence in donor populations is high and Bd infection intensity (load) is below the level at which frog mortality is predicted (calculate mean prevalence and load). Recipient sites to which frogs were translocated were chosen based on previous *R. sierrae* presence (determined from VES and/or museum records) or characteristics that suggested high quality habitat for this species (Knapp 2005).

@@

In this model we ignore density-dependent recruitment because we were interested in the growth of the population from an initial reintroduction and whether this growth was sufficient to prevent extinction over 50 years following the introduction. We also did not directly consider the dynamics of Bd in this model. We made this decision because i) all translocated populations are infected with Bd at high prevalence ii) host density does not seem to play a significant role in multi-year Bd infection dynamics in this system (Wilber et al. 2022). Thus, ignoring Bd infection dynamics and instead assuming all host vital rates are in the presence of high Bd prevalence significantly simplifies the model without much loss of realism.
